Functional Pearl: Short and Mechanized Logical Relation for Dependent Type Theories

### 2024-02-27 paper/paper.tex
midstream check in in 8.2

\newcommand\dheader[1]{\rotatebox{60}{{#1}}}
\newcommand\header[1]{\rotatebox{90}{{#1}}}

@@

% \begin{minipage}{0.8\textwidth}
  \begin{tabular}{ l |  l  | l | l | l }
      & \header{Universes} & \header{Inductives} & \header{Conversion}
      & \header{Large Elim} \\
    \hline
    \lang{} & $\mathbb{N}$ & Id, Bool & U & {\boxedsymbols ✓} \\
    % \hline
    $\lambda^\theta$ & 0 & Id, Nat & U & {\boxedsymbols ✗}\\
    NBE-in-Coq & 1 & Nat & T & {\boxedsymbols ✗} \\
    % \hline
    $\lambda^{\Pi U\mathbb{N}}$ & 1 & Nat & T & {\boxedsymbols ✓} \\
    % \hline
    MLTT-a-la-Coq & 1 & Id, Nat & T & {\boxedsymbols ✓} \\
    % \hline
    Core Nuprl & $\mathbb{N}$ & W-Types & E & {\boxedsymbols ✓} \\
    % \hline
    % CIC & $\mathbb{I}$,$\mathbb{N}$ & General & U & {\boxedsymbols ✓}\\
    % CoreSpec & \\
    % PCUIC & \\
    %   & \lang{} & \citet{anand2014towards} &
    %                                          \citet{barras2012semantical}
    % & \citet{martin-lof-a-la-coq}  \\
    % \hline
    % Universe & Countable & Countable & Impredicative + Countable & One\\
    % % \hline
    % % Large Elimination & {\boxedsymbols ✓} & {\boxedsymbols ✓} & {\boxedsymbols ✓} \\
    % \hline
    % Inductive Types & Id, Bool & W types & General inductive types & Nat \\
    % \hline
    % Convertibility & Untyped & Untyped,Extensional & Untyped & Typed \\
  \end{tabular}
% \end{minipage}

  \begin{tabular}{ll}
  \\
    $\lambda^\theta$  & \citet{casinghino:combining-proofs-programs} (logical fragment only) \\
    NBE-in-Coq& \citet{nbeincoq} \\
    $\lambda^{\Pi U\mathbb{N}}$ &\citet{decagda} \\
    MLTT-a-la-Coq &\citet{martin-lof-a-la-coq} \\
    Core Nuprl &\citet{anand2014towards} \\
    CIC &\citet{barras2012semantical} \\
    CoreSpec & \\
    PCUIC & \\

  \\
  Universes: &Countable ($\mathbb{N}$), Zero (0), One (1), Impredicative ($\mathbb{I}$) \\
  Conversion:& Typed (T), Untyped (U), Extensional (E) \\
  \end{tabular}

>>>>

%\newcommand\dheader[1]{\rotatebox{60}{{#1}}}
\newcommand\header[1]{\rotatebox{60}{{#1}}}

@@

% \begin{minipage}{0.8\textwidth}
  \begin{tabular}{| l |  l  | l | l | l | }
    \hline
      & \header{Universes} & \header{Inductives} & \header{Conversion}
      & \header{Large Elim} \\
    \hline
    \lang{} (this work) & $\mathbb{N}$ & Id, Bool & U & {\boxedsymbols ✓} \\
    % \hline
    $\lambda^\theta$ & 0 & Id, Nat & U & {\boxedsymbols ✗}\\
    NBE-in-Coq & 1 & Nat & T & {\boxedsymbols ✗} \\
    % \hline
    $\lambda^{\Pi U\mathbb{N}}$ & 1 & Nat & T & {\boxedsymbols ✓} \\
    % \hline
    MLTT-a-la-Coq & 1 & Id, Nat & T & {\boxedsymbols ✓} \\
    % \hline
    Core Nuprl & $\mathbb{N}$ & W-Types & E & {\boxedsymbols ✓} \\
    \hline 
    % CIC & $\mathbb{I}$,$\mathbb{N}$ & General & U & {\boxedsymbols ✓}\\
    % CoreSpec & \\
    % PCUIC & \\
    %   & \lang{} & \citet{anand2014towards} &
    %                                          \citet{barras2012semantical}
    % & \citet{martin-lof-a-la-coq}  \\
    % \hline
    % Universe & Countable & Countable & Impredicative + Countable & One\\
    % % \hline
    % % Large Elimination & {\boxedsymbols ✓} & {\boxedsymbols ✓} & {\boxedsymbols ✓} \\
    % \hline
    % Inductive Types & Id, Bool & W types & General inductive types & Nat \\
    % \hline
    % Convertibility & Untyped & Untyped,Extensional & Untyped & Typed \\
  \end{tabular}

  \begin{tabular}{ll}
  \textbf{Features:} \\
  Universes: & Countable ($\mathbb{N}$), Zero (0), One (1), Impredicative ($\mathbb{I}$) \\
  Inductives: & Identity types (Id), Natural numbers (Nat), W-types~\cite{w-types} \\
  Conversion:& Typed (T), Untyped (U), Extensional (E) \\
    \\
  \textbf{Citations:}\\
  $\lambda^\theta$  & \citet{casinghino:combining-proofs-programs} (logical fragment only) \\
  NBE-in-Coq& \citet{nbeincoq} \\
  $\lambda^{\Pi U\mathbb{N}}$ &\citet{decagda} \\
  MLTT-a-la-Coq &\citet{martin-lof-a-la-coq} \\
  Core Nuprl &\citet{anand2014towards} \\
  \end{tabular}
